PANCHANGE_analysis

### 2021-05-14 PANCHANGE_analysis.Rmd

    align = "v",
    nrow = 6,
    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
    hjust = c(0,0,0,0,0,0),
    vjust = c(2,0,0,0,0,0)
  ),
  as_ggplot(cowplot::get_legend(
    lm.forest(data %>% filter(Categories=="Other"), title="") +
      theme(legend.position = c(0.65,0.5),
            legend.direction = "horizontal",
            legend.box = "horizontal",
            legend.box.just = "centre",
            legend.title = element_blank(),
            legend.text = element_text(size = plot_text_size)) +
      guides(color = guide_legend(order = 1, reverse = T))
  )),
  ncol= 1,
  nrow = 2,
  rel_heights = c(1, 0.05)
)

@@

plot_grid(
  plot_grid(
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Preexisting mental health"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Gender"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Age"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Ethnicity"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Employment"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
      theme(
        axis.title.x = element_text(size = plot_text_size),
        axis.text.x = element_text(size = plot_text_size)),

    align = "v",
    nrow = 6,
    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
    hjust = c(0,0,0,0,0,0),
    vjust = c(2,0,0,0,0,0)
  ),
  as_ggplot(cowplot::get_legend(
    lm.forest(data %>% filter(Categories=="Other"), title="") +
      theme(legend.position = c(0.65,0.5),
            legend.direction = "horizontal",
            legend.box = "horizontal",
            legend.box.just = "centre",
            legend.title = element_blank(),
            legend.text = element_text(size = plot_text_size)) +
      guides(color = guide_legend(order = 1, reverse = T))
  )),
  ncol= 1,
  nrow = 2,
  rel_heights = c(1, 0.05)
)

>>>>

    align = "v",
    nrow = 6,
    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
    hjust = c(0,0,0,0,0,0),
    vjust = c(2,0,0,0,0,0)
  ),
  as_ggplot(cowplot::get_legend(
    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
      theme(legend.position = c(0.65,0.5),
            legend.direction = "horizontal",
            legend.box = "horizontal",
            legend.box.just = "centre",
            legend.title = element_blank(),
            legend.text = element_text(size = plot_text_size)) +
      guides(color = guide_legend(order = 1, reverse = T))
  )),
  ncol= 1,
  nrow = 2,
  rel_heights = c(1, 0.05)
)

@@

plot_grid(
  plot_grid(
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Pre-existing mental health"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Gender"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Age"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Ethnicity"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Employment"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
      theme(
        axis.title.x = element_text(size = plot_text_size),
        axis.text.x = element_text(size = plot_text_size)),

    align = "v",
    nrow = 6,
    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
    hjust = c(0,0,0,0,0,0),
    vjust = c(2,0,0,0,0,0)
  ),
  as_ggplot(cowplot::get_legend(
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
      theme(legend.position = c(0.65,0.5),
            legend.direction = "horizontal",
            legend.box = "horizontal",
            legend.box.just = "centre",
            legend.title = element_blank(),
            legend.text = element_text(size = plot_text_size)) +
      guides(color = guide_legend(order = 1, reverse = T))
  )),
  ncol= 1,
  nrow = 2,
  rel_heights = c(1, 0.05)
)
